A preliminary constraint grammar for Russian

### 2015-05-07 2015-nodalida-ruscg/presentation_ruscg.tex
mroe slides for HMM
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60295 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{frame}
\frametitle{}
\framesubtitle{}
\begin{itemize}
	\item 
	\pause
	\item 
	\begin{itemize}
		\item 
		\pause
	\end{itemize}
	\item 
\end{itemize}
\end{frame}

\section{Conclusions and future work} %FRAN
\begin{frame}
\frametitle{}
\framesubtitle{}
\begin{itemize}
	\item 
	\pause
	\item 
	\begin{itemize}
		\item 
		\pause
	\end{itemize}
	\item 
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Combining CG with HMM tagger}
\framesubtitle{}
\begin{itemize}
	\item CG removes less than half of ambiguity
	\pause
	\item To resolve remaining ambiguity, we backoff to HMM tagger
	\begin{itemize}
		\item This approach has been applied with...\\
		Basque \cite{ezeiza.ea-98},\\
		Czech \cite{hajic.ea-01,hajic.ea-07},\\
		Norwegian \cite{johannessen.ea-11,johannessen.ea-12},\\
		Spanish \cite{hulden12},\\
		and Turkish \cite{oflazer.tur-96}
		\pause
	\end{itemize}
	\item We follow the voting method used by \cite{hulden12}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Voting setup}
\framesubtitle{}
\begin{itemize}
	\item Freely available hunpos tagger
	\pause
	\item 10-fold cross-validation (90\% training, 10\% testing)
	\pause
	\item 3 configurations
	\begin{itemize}
		\item HMM - hunpos with default options
		\pause
		\item HMM+Morph - incorporating FST output as full-form lexicon
		\pause
		\item HMM+Morph vs CG - Voting setup: if constraint grammar left 1 valid reading,
		take that. Otherwise, take output of HMM+Morph.
	\end{itemize}
	\item 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Voting results}
\framesubtitle{}
\begin{figure}
  \centering
  \includegraphics[width=0.70\textwidth]{graphics/learning-curve.pdf}
  %\caption{Learning curve for three taggers, \texttt{hunpos} with no lexicon, 
  %  \texttt{hunpos} with a lexicon, and \texttt{hunpos} with a lexicon and the 
  %  Russian constraint grammar in a voting set up.}
  \label{fig:curve}
\end{figure}
\begin{itemize}
	\item hunpos tagger alone is more dependent on training-corpus size
	\pause
	\item 
	\pause
	\item 
	\item 
\end{itemize}
\end{frame}

\section{Future work and conclusions} %FRAN

\begin{frame}
\frametitle{Future work}
\framesubtitle{}
\begin{itemize}
	\item Improve precision while maintaining high recall
	\pause
	\item Add syntactic functions and dependency parsing
	\begin{itemize}
		\item We plan to use Giellatekno's dependency parser \cite{antonsen10}
		\pause
	\end{itemize}
	\item Improve workflow by extending our gold-standard corpus while checking new rule accuracy
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Conclusions}
\framesubtitle{}
\begin{itemize}
	\item Preliminary constraint grammar for Russian
	\pause
	\begin{itemize}
		\item Tuned for high recall at expense of precision
		\pause
		\item Rules are assigned to levels, based on tested accuracy
		\pause
		\item Improves performance of trigram HMM-based tagger
		\pause
	\end{itemize}
	\item Improve workflow by extending our gold-standard corpus while checking new rule accuracy
\end{itemize}
\end{frame}
